---
title: "Final Project Wine Summary Statistics"
author: "Jessie Pao"
subtitle:
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}

# Please leave this code chunk as is. It makes some slight formatting changes to alter the output to be more aesthetically pleasing. 

library(knitr)

# Change the number in set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# this sets text outputted in code chunks to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = FALSE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               # change fig.width and fig.height to change the code height and width by default
               fig.width = 5.5,  
               fig.height = 4.5,
               fig.align='center')


```

```{r setup-2}

# Always print this out before your assignment
sessionInfo()
getwd()

```


<!-- ### start answering your problem set here -->
<!-- You may export your homework in either html or pdf, with the former usually being easier. 
     To export or compile your Rmd file: click above on 'Knit' then 'Knit to HTML' -->
<!-- Be sure to submit both your .Rmd file and the compiled .html or .pdf file for full credit -->


```{r setup-3}

# load all your libraries in this chunk 
library(tidyverse)
library(Hmisc)
library('photobiology')
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidytext)
library(wordcloud)
library(reshape2)
library('randomForest')
library(reshape2)
library(partykit)
library(PerformanceAnalytics)
library(rpart)       
library(rpart.plot)  

```



Load in wine data set
```{r}

wine_DF <- 
  read.csv(here::here("dataset",
           "wine.csv"))

wine_DF

```

Clean up wine data set to get rid of rows with NA values and remove some columns 
```{r}

wine_clean <- wine_DF %>% na.omit()

wine_clean

```


Summary of wine data set
```{r}

summary(wine_clean)

```


Box plot of the quality of all of the wines
Lowest quality is 3, highest quality is 8. 
Q1 is 5, the median and Q3 are at 6, the min is 4 and the max is 7 with outliers at 3 and 8.
The cutoff for a good wine would be at 6.
```{r}

p <- ggplot(wine_clean, aes(x=quality)) + 
  geom_boxplot()
p

```

```{r}

wine_clean <- wine_clean %>% 
  mutate(quality = ifelse(quality > 5 , 1, 0))

wine_clean <- wine_clean %>% 
  mutate(quality = factor(quality))

wine_clean

```


Correlation Matrix
```{r}

cor_wine <- round(cor(wine_clean),2)
head(cor_wine)

```


Remove the upper triangle of data (The data is repeated so it isn't important)
```{r}

get_upper_tri <- function(cor_wine){
    cor_wine[lower.tri(cor_wine)]<- NA
    return(cor_wine)
}

reorder_cor_wine <- function(cor_wine){
# Use correlation between variables as distance
dd <- as.dist((1-cor_wine)/2)
hc <- hclust(dd)
cor_wine <-cor_wine[hc$order, hc$order]
}

```


Reshape the correlation matrix
```{r}

#cor_wine <- reorder_cor_wine(cor_wine)

upper_tri <- get_upper_tri(cor_wine)
upper_tri

melted_cor_wine <-  melt(upper_tri, na.rm = TRUE)
head(melted_cor_wine)

```


Graph of the maximum points of wines from each country
```{r}

ggplot(melted_cor_wine, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Wine\nCorrelation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))+
 coord_fixed()

```



Random Forest Model


Run a random forest model.  From the graph we can see that this model is better at predicting if a bottle of wine is high quality. 
```{r}

wine_rf <- randomForest(quality ~ .,
                       data = wine_clean,
                       type = classification,
                       mtry = 4,
                       na.action = na.roughfix,
                       ntree = 100, 
                       importance = TRUE)

print(wine_rf)

plot(wine_rf)


```


Tune the random forest model to determine what the optimal parameters (mtry) are.
From the graph we can see that an mtry of 7 would give us the least amount of error
```{r}

rf_mods <- list()
oob_err <- NULL
test_err <- NULL
for(mtry in 0:11){
  rf_fit <- randomForest(quality ~ ., 
                         data = wine_clean,
                         mtry = mtry,
                         na.action = na.roughfix,
                         ntree = 20)
  oob_err[mtry] <- rf_fit$err.rate[20]
  
  cat(mtry," ")
}

oob_err

results_DF <- data.frame(mtry = 1:11, oob_err)
ggplot(results_DF, aes(x = mtry, y = oob_err)) + geom_point() + theme_minimal()

```


Now if we rerun the random forest model with an mtry of 2 the error has decreased compared to the above model with a mtry of 4. 
```{r}


wine_rf <- randomForest(quality ~ .,
                       data = wine_clean,
                       type = classification,
                       mtry = 2,
                       na.action = na.roughfix,
                       ntree = 100, 
                       importance = TRUE)

print(wine_rf)

plot(wine_rf)


```



```{r}



```